### 2020-05-08 README.Rmd
more cosmetic changes
added new doi retrieving function; implemented more changes to vignette

# dataaimsr <img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>

@@

`dataaimsr` is the **AIMS Data Platform R Client** will provide easy access to data sets for R applications to the [AIMS Data Platform API](https://aims.github.io/data-platform).

@@

The API Key can be passed to the package functions as an additional `api_key = 'XXXX'` argument, however it is preferred that API Keys are not stored in code.

@@

At this stage **AIMS Data Platform R Client** is not hosted on CRAN R package network.
An alternative method of installation is to use the R `devtools` package.

@@

After `devtools` has been installed the **AIMS Data Platform R Client** can be installed directly
from GitHub using the following command:

@@

The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data. Documentation about available data sets can be found on the [AIMS Data Platfom API](https://aims.github.io/data-platform).

@@

Further information about the **AIMS DataPlatform R Client** and **AIMS DataPlatform API** can be seen on the [project page](https://aims.github.io/data-platform-r).

This library is provided for use under the Creative Commons by Attribution license ([CC BY 3.0](https://creativecommons.org/licenses/by/3.0/au/legalcode)) by the AIMS Datacentre for the [Austrailian Institute of Marine Science](https://www.aims.gov.au)

>>>>

# dataaimsr <img src="man/figures/logo.png" width = 180 alt="dataaimsr Logo" align="right" />

@@

`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://aims.github.io/data-platform).

@@

The API Key can be passed to the package functions as an additional `api_key = 'XXXX'` argument, however it is preferred that API Keys are not stored permanently in your machine.

@@

At this stage `dataaimsr` is not hosted on CRAN R package network.
An alternative method of installation is to use the R `devtools` package.

@@

After `devtools` has been installed `dataaimsr` can be installed directly from GitHub using the following command:

@@

The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data. Documentation about available data sets can be found on the [AIMS Data Platform API](https://aims.github.io/data-platform).

@@

Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://aims.github.io/data-platform-r).

This library is provided for use under the Creative Commons by Attribution license ([CC BY 3.0](https://creativecommons.org/licenses/by/3.0/au/legalcode)) by the AIMS Datacentre for the [Australian Institute of Marine Science](https://www.aims.gov.au)
